Robotic Cart System

### 2021-05-10 parts/10-introduction.tex
Added assembly instructions appendix

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
\begin{itemize}
    \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
    \item Chapter \ref{ch: sysArchitecture} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
    \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
    \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
    \item Appendix \ref{ch: coppSimModeling} goes through the steps to build and simulate the Budget Bot chassis in CoppeliaSim
\end{itemize}

>>>>

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
\begin{itemize}
    \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
    \item Chapter \ref{ch: sysDesign} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
    \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
    \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
    \item Appendix \ref{ch: coppSimModeling} goes through the steps to build and simulate the Budget Bot chassis in CoppeliaSim
\end{itemize}
